Binary companions of evolved stars in \apogee\ \DR: \\ Search method and catalog of $\sim$5,000 companions

### 2018-04-09 paper/1-catalog/twoface-catalog.tex
ampersand
moar authors

% APOGEE RV var co-authors
\author{Nathan De Lee}
\affiliation{Department of Physics, Geology, and Engineering Technology, Northern Kentucky Univerity, Highland Heights, KY 41099}
\affiliation{Department of Physics & Astronomy, Vanderbilt University, Nashville, TN 37235}

@@

\author{Domingo An\'ibal Garc\'ia-Hern\'andez}
\affiliation{Instituto de Astrof\'isica de Canarias, 38205 La Laguna, Tenerife, Spain}

@@

\author{Olga Zamora}
\affiliation{Instituto de Astrof\'isica de Canarias, 38205 La Laguna, Tenerife, Spain}

@@

HWR acknowledges support by Sonderforschungsbereich SFB 881 (A3) of the German
Research Foundation (DFG), and from the European Research Council under the
European Union’s Seventh Framework Programme (FP 7) ERC Grant Agreement
n. [321035].

>>>>

% APOGEE RV var co-authors
\author{Nathan De Lee}
\affiliation{Department of Physics, Geology, and Engineering Technology, Northern Kentucky Univerity, Highland Heights, KY 41099}
\affiliation{Department of Physics \& Astronomy, Vanderbilt University, Nashville, TN 37235}

@@

\author{Domingo A. Garc\'ia-Hern\'andez}
\affiliation{Instituto de Astrof\'isica de Canarias (IAC), E-38205 La Laguna, Tenerife, Spain}
\affiliation{Universidad de La Laguna (ULL), Departamento de Astrof\'isica, E-38206 La Laguna, Tenerife, Spain}

@@

\author{Jennifer Sobeck}
\affiliation{Department of Astronomy, University of Washington, Box 351580,
Seattle, WA 98195, USA}

\author{Olga Zamora}
\affiliation{Instituto de Astrof\'isica de Canarias (IAC), E-38205 La Laguna, Tenerife, Spain}
\affiliation{Universidad de La Laguna (ULL), Departamento de Astrof\'isica, E-38206 La Laguna, Tenerife, Spain}

@@

DWH was partially supported by the NSF (grant AST-1517237).
HWR acknowledges support by Sonderforschungsbereich SFB 881 (A3) of the German
Research Foundation (DFG), and from the European Research Council under the
European Union’s Seventh Framework Programme (FP 7) ERC Grant Agreement
n. [321035].
DAGH and OZ acknowledge support provided by the Spanish Ministry of Economy and
Competitiveness (MINECO) under grant AYA-2017-88254-P.
